Stack Safety as a Security Property

### 2020-07-05 main.tex
Remove the last element of prefix-up-to

\paragraph*{Prefix-Up-To}
The ``prefix-up-to'' operation \(\PUT(\Trace,f)\) \bcp{Wouldn't
  ``While'' be more mnemonic?}  takes a trace \(T\) and a predicate on
elements \(f\) and gives the prefix of \(T\) ending with the first
element on which \(f\) holds, coinductively:

\begin{center}
\begin{minipage}{.3\textwidth}
\judgment{\(f\ \traceelem\)}
         {\(\PUT(f,\traceelem\Trace) = \traceelem\)}
\end{minipage}
%
\begin{minipage}{.3\textwidth}
\judgment{}
         {\(\PUT(f,\traceelem) = \traceelem\)}
         %
\end{minipage}
\begin{minipage}{.3\textwidth}
\judgmenttwo{\(\neg f\ \traceelem\)}{\(\PUT(f,\Trace) = \Trace'\)}
            {\(\PUT(f,\traceelem\Trace) = \traceelem\Trace'\)}
\end{minipage}
\end{center}
%
Note that if the resulting trace is a strict prefix of the parameter, then the
predicate must hold on its final element. If the predicate never holds,
\(\PUT\) is the identity function.

@@

\bcp{Can we please call it something else?  An
  ``equivalence'' should always be transitive.}
\sna{Similarity seems less loaded?}
\[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

>>>>

\paragraph*{Until}
The ``Until'' operation \(\PUT(\Trace,f)\) \bcp{Wouldn't
``While'' be more mnemonic?} \sna{Appealing, but it's more of a
``while-not''? Trying out ``until''. In any case... moving away
from doing joins means this needs to get some work to eliminate
the trailing observation. Here's an attempt.} takes a trace
\(\Trace : \mathit{trace} \TRACEELEMS \times \OBSS\) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.
Subtly, because the observation associated with a trace represents its
next step, when we take a prefix from a trace containing observations
we must replace the final observation with a \(\tau\).

  \begin{center}
  \begin{minipage}{.3\textwidth}
    \judgment{\(f\ \traceelem\)}
             {\(\PUT(f,(\traceelem,\obs)\Trace) = (\traceelem,\tau)\)}
  \end{minipage}
%
  \begin{minipage}{.3\textwidth}
  \judgment{}
           {\(\PUT(f,(\traceelem,\obs)) = (\traceelem,\tau)\)}
%
  \end{minipage}
  \begin{minipage}{.3\textwidth}
  \judgmenttwo{\(\neg f\ \traceelem\)}{\(\PUT(f,\Trace) = \Trace'\)}
              {\(\PUT(f,(\traceelem,\obs)\Trace) = (\traceelem,\obs)\Trace'\)}
  \end{minipage}
  \end{center}
%
Note that if the resulting trace is a strict prefix of the parameter, then the
predicate must hold on its final element. If the predicate never holds,
\(\PUT\) is the identity function.

@@

\bcp{Can we please call it something else?  An
  ``equivalence'' should always be transitive.}
\sna{Similarity seems less loaded?}
\[\obsT_1 \simeq \obsT_2 \triangleq \obsT_1 \lesssim \obsT_2 \land \obsT_2 \lesssim \obsT_1\]
